Parameterized convection, grid-scale clouds and resolution sensitivity in the Community Atmosphere Model

### 2019-08-19 resolution.tex
edits

\begin{figure}
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_cape.pdf}\\
\end{center}
\caption{(a) Dilute CAPE computed from time mean temperature and moisture profiles of ascending (red), subsiding (blue) and all grid columns (black) in the deep tropics ($\pm 10^{\circ}$ latitude), and (b) space-time weights of ascending (red) and descending (blue) grid columns in the deep tropics. (c) Dilute CAPE computed for ascending/descending grid columns, but using the mean temperature profile for the entire deep tropics, (d) Same as (c) but using the mean moisture profile for the entire deep tropics. (e) Same as (c) but using the fixing the temperature to the $ne20$ profiles, and (f) same as (d) but fixing the moisture to the $ne20$ profiles. Grey crosses in (a) are dilute CAPE derived from the sum of the products of space-time weights with the dilute CAPE values of ascending/descending grid columns.}
\label{fig:cape}
\end{figure}

@@

Table~\ref{tbl:table2} indicates that the $\pm 15^{\circ}$ latitude band accounts for most of the change in global mean stratiform precipitation with resolution, and so $\overline{R_s}$ is defined as the mean over the $\pm 15^{\circ}$ latitude region. Figure~\ref{fig:pdecomp} is a plot of the terms $M_s \left( \omega_i , q_j \right)$ and $f_s \left( \omega_i , q_j \right) M_s \left( \omega_i , q_j \right)$ for all resolutions,. The plots are computed using 6-hourly instantaneous output of $\omega_{i}$ and $q_{j}$, with 0.05 Pa/s and 0.4 g/kg bins. Values in  $\left( \omega_{i} , q_{j} \right)$ space are only shown for bins with $f_s \geq1 \times 10^{-5}$, a reasonable cut-off to a bins' contribution to $\overline{R_s}$. The $M_s$ plots show that larger magnitude $\omega_{850}$ correspond to larger magnitude time-mean stratiform precipitation rates, and these larger precipitation rates are associated with larger spatial frequencies $f_s \left( \omega_i , q_j \right)$ at higher resolutions. These large magnitude stratiform precipitation rates increasingly contribute to the increase in $\overline{R_{s}}$ with resolution, as seen by the expansion of $f_s \left( \omega_i , q_j \right) M_s \left( \omega_i , q_j \right)$ to include larger magnitude $\omega_{850}$. Changes to the time mean spatial frequency of the $q_{850}$ field contributes comparatively much less to changes in stratiform precipitation.

>>>>

\begin{figure}
\begin{center}
\noindent\includegraphics[width=20pc,angle=0]{figs/temp_cape.pdf}\\
\end{center}
\caption{(a) Dilute CAPE computed from time mean temperature and moisture profiles of ascending (red), subsiding (blue) and all grid columns (black) in the deep tropics ($\pm 10^{\circ}$ latitude), and (b) space-time weights of ascending (red) and descending (blue) grid columns in the deep tropics. (c) Dilute CAPE computed for ascending/descending grid columns, but using the mean temperature profile for the entire deep tropics, (d) Same as (c) but using the mean moisture profile for the entire deep tropics. (e) Same as (c) but fixing temperature to the $ne20$ profiles, and (f) same as (d) but fixing moisture to the $ne20$ profile. Grey crosses in (a) are dilute CAPE derived from the sum of the products of space-time weights with the dilute CAPE values of ascending/descending grid columns.}
\label{fig:cape}
\end{figure}

@@

Table~\ref{tbl:table2} indicates that the $\pm 15^{\circ}$ latitude band accounts for most of the change in global mean stratiform precipitation with resolution, and so $\overline{R_s}$ is defined as the mean over the $\pm 15^{\circ}$ latitude region. Figure~\ref{fig:pdecomp} is a plot of the terms $M_s \left( \omega_i , q_j \right)$ and $f_s \left( \omega_i , q_j \right) M_s \left( \omega_i , q_j \right)$ for all resolutions,. The plots are computed using 6-hourly instantaneous output of $\omega_{i}$ and $q_{j}$, with 0.05 Pa/s and 0.4 g/kg bins. Values in  $\left( \omega_{i} , q_{j} \right)$ space are only shown for bins with $f_s \geq1 \times 10^{-5}$, a reasonable cut-off to a bins' contribution to $\overline{R_s}$. The $M_s$ plots show that larger magnitude $\omega_{850}$ correspond to larger magnitude time-mean stratiform precipitation rates, and these larger precipitation rates are associated with larger spatial frequencies $f_s \left( \omega_i , q_j \right)$ at higher resolutions. These large magnitude stratiform precipitation rates increasingly contribute to the increase in $\overline{R_{s}}$ with resolution, as seen by the increase in $f_s \left( \omega_i , q_j \right) M_s \left( \omega_i , q_j \right)$ in the larger magnitude $\omega_{850}$ space with resolution. Changes to the time mean spatial frequency of the $q_{850}$ field contributes comparatively much less to changes in stratiform precipitation.
